Julia for HPC: In Situ Data Analysis with Julia for Climate Simulations at Large Scale

### 2023-09-18 paper/paper.tex
Update paper.tex

\usepackage{amsmath}
%\usepackage[ruled,vlined]{algorithm2e}
%\usepackage{algorithm, algorithmic}

@@

>>>>

\usepackage{amsmath}
%\usepackage[ruled,vlined]{algorithm2e}
\usepackage{algorithm}
\usepackage[noend]{algpseudocode}
\renewcommand{\algorithmicrequire}{\textbf{Input:}}
\renewcommand{\algorithmicensure}{\textbf{Output:}}

@@

\begin{algorithm}
\caption{In situ algorithm for SSW detection.}\label{ssw_algo}
\begin{algorithmic}[1]
\Require{EAM simulation data.} 
\Ensure{A list of time steps and corresponding simulation years when SSW is detected.}
\Statex
\For{each EAM time\_step}
  \If{(current\_time\_step == end\_of\_day)}
    \State Compute partial zonal mean zonal wind values at each MPI process.
    \State Compute the global zonal mean zonal wind with MPI:Reduction.
    \If{(global zonal mean zonal wind < 0)}
    \State counter=counter+1
    \EndIf
    \If{((counter == 10))}
    \State Record current time step as the beginning of a SSW event.
    \State counter=0
    \EndIf
  \Else
    \State continue
  \EndIf
\EndFor
\end{algorithmic}
\end{algorithm}
